---
title: "## Global Peace Index"
subtitile: "Coursera Developing Data Products"
author: "Martin Sliva"
date: "2018 August 5"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Global Peace Index

The Global Peace Index analyses the state of peace around the world as an attempt to measure the relative position of nations peacefulness. 

__Exploratory goal:__ Have religions or religiosity any impact on peace?

Data  used  
*Global Peace Index* - which describes peacefulness of a country. Lower values means more peaceful country.  
*Religion - religion* with most follower in country  
*Religoisity* - measures how much is religion important for people in a country   

Let's get those infromation together a explore what data tell us.



## Peace index by religiosity 

```{r  echo = FALSE, warning=FALSE, message=FALSE}
library(plotly)


index <- read.csv("gpi.csv")

plot_ly(data = index,  x= ~Index, type = "box", color =  ~Religiosity, hoverinfo = 'text',
text = ~paste('Country: ', Country,
'</br></br> Index: ', Index,
'</br> Ranking: ', Ranking,
'</br> Religion: ', Religion))


```

## Peace index by majority religion
```{r echo = FALSE, warning=FALSE, message=FALSE}

plot_ly(data = index,  y= ~Index, x= ~Ranking, color = ~Religion, type= "scatter",mode="markers",  hoverinfo = 'text',
text = ~paste('Country: ', Country,
'</br></br> Index: ', Index,
'</br> Ranking: ', Ranking,
'</br> Religiosity: ', Religiosity))


```


## Explore the map

Now, we have the first impression how Peaceful index is related to religion and religiosity.

But we are talking about countries. I would be nice to see it on the map to get better imagination.

So let's jump to my shine app: https://msliva.shinyapps.io/Global_Peace_Index/ (and please be patient - the first loading may take some time - 20 sec.)

Enjoy your explorataion and make your own findings.

Data sources are describes in tab "Description".