---
title: "Shiny Application and Reproducible Pitch"
author: "Martin Slíva"
date: "2018 M07 28"
output: ioslides_presentation
theme: "uulm"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Regresion on mtcars dataset

Application displays chart which shows linear regression for mpg and choosen predictor. In the title of chrart there is printed the formula for regression line.

The user can  chose a predictor form select box.

The application uses standard mtcars dataset from R. 

Server side application calculates the linear regression for outcome mpg and chosen predictor. 



## Main function in server.R - code

```{r , eval=FALSE, echo=TRUE}
      output$distPlot <- renderPlot({
    
    # input from ui.R
    j <- as.numeric(input$select)

    model <- lm(mtcars[,i]~mtcars[,j])
    Intercept <- model[[1]][1]
    Slope <- model[[1]][2]
    
    plot(y=mtcars[,i], x=mtcars[,j], type="p",
         xlab = a[j], ylab = a[i], 
         main = paste(a[i]," = (", round(Intercept,3), ") + 
                      (", round(Slope,3), ")*", a[j]), col="blue")
    +abline(Intercept,Slope, col="red")

  })

```

## Default chart in application

```{r cars, echo = FALSE}
    data("mtcars")
    a <- names(mtcars)
    i <- 1
    j <- 2
    model <- lm(mtcars[,i]~mtcars[,j])
    Intercept <- model[[1]][1]
    Slope <- model[[1]][2]
    
    plot(y=mtcars[,i], x=mtcars[,j], type="p", xlab = a[j], ylab = a[i], main = paste(a[i]," = (", round(Intercept,3), ") + (", round(Slope,3), ")*", a[j]), col="blue")+abline(Intercept,Slope, col="red")

```

## Links

The link to app https://msliva.shinyapps.io/develdataprod/

The link to GIT: https://github.com/martinsliva/coursera_ddp_final

